NHL Realignment Effects on Playoff Qualification

### 2020-12-14 Paper.Rmd
fix small errors

## Introduction
  In 2011 when the Atlanta Thrashers became the Winnipeg Jets. A problem was presented as Winnipeg is considerably far from the east coast of the North American continent. Because of this and how the season is set up, the average travel time for teams playing winnipeg were fairly large as eastern conference teams play each other more often. Just before the start of the 2013-14 season, the league offices for the NHL decided to move over the Winnipeg Jets from the Eastern conference to the Western conference and in return the Eastern conference aquired the Columbus Blue Jackets and the Detroit Redwings. This left the the two conferences at an uneven balance. The Eastern conference now had sixteen teams while the Western conference only had fourteen teams. This presented a curious problem as for both conferences, eight teams make the playoff brackets. It is easy to see the problem at hand that the western conference has just as many playoff slots for having two less teams. The goal of our analysis and the paper we based our ideas off of and partially replicated, was to discover what that difference could mean in the grander sense of the league moving forward with this set up. We did this based on the average points and wins necessary to make the playoffs for both conferences.

>>>>

## Introduction
  In 2011 the Atlanta Thrashers became the Winnipeg Jets. A problem was presented as Winnipeg is considerably far from the east coast of the North American continent. Because of this and how the season is set up, the average travel time for teams playing winnipeg were fairly large as eastern conference teams play each other more often. Just before the start of the 2013-14 season, the league offices for the NHL decided to move over the Winnipeg Jets from the Eastern conference to the Western conference and in return the Eastern conference aquired the Columbus Blue Jackets and the Detroit Redwings. This left the the two conferences at an uneven balance. The Eastern conference now had sixteen teams while the Western conference only had fourteen teams. This presented a curious problem as for both conferences, eight teams make the playoff brackets. It is easy to see the problem at hand that the western conference has just as many playoff slots for having two fewer teams. The goal of our analysis and the paper we based our ideas off of and partially replicated, was to discover what that difference could mean in the greater sense of the league moving forward with this set up. We did this based on the average points and wins necessary to make the playoffs for both conferences.
